\documentclass[10pt]{article}

\usepackage[a4paper, total={7in, 10in}]{geometry} % define page size
\usepackage{hyperref} % for linked in ref
\usepackage{array, xcolor} % for colour
\usepackage{eurosym} % for the euro symbol
\usepackage{enumitem} % http://ctan.org/pkg/enumitem
\usepackage{longtable} % multi page table
\usepackage{fontawesome} % for symbols

\definecolor{lightgray}{gray}{0.8}

\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\title{\bfseries\Huge Rhydian Jenkins}

\date{}
\author{}

\begin{document}

\maketitle \vspace{-7em}

% Contact Details
\section*{}
\faLinkedin \quad \href{https://www.linkedin.com/in/rhydian-jenkins-30309085/}{LinkedIn.com/in/rhydian-jenkins-30309085}\\
\faGithub \quad \href{https://github.com/RhydianJenkins}{GitHub.com/RhydianJenkins}\\
\faPhone \quad 07384 629 336\\
\faEnvelope \quad Rhydz@msn.com\\
\faMapMarker \quad SA11 2LS

\section*{Personal Profile}
Computer Science PhD and Software Engineer with a strong track record of delivering high-quality software. Experienced across multiple languages, technologies, and development environments.
A collaborative problem-solver who works effectively both independently and within teams, with a strong commitment to continuous learning and tackling new challenges.

\section*{Skills}
\begin{itemize} \setlength\itemsep{-0.25em}
    \item DevOps (Docker, Jenkins, Kubernetes, Git, GCP, AWS)
    \item Front end - Webpack, Vite, Next, Nuxt and SvelteKit
	\item Back end - Full stack and microkernel Symfony, Laminas, and Laravel
    \item Package management and build tools (npm, Nix, Composer, Docker-compose, Maven, Make, etc)
	\item Public speaking while presenting work at various conferences
\end{itemize}

% experience
\section*{Experience}
\begin{longtable}{L!{\VRule}R}

% Basekit
{\bf BaseKit}\\
2022--present\\
&{\bf Full Stack Developer}\newline
Accountable for developing and maintaining software for a large white label website builder monorepo. My responsibilities included working on various applications such as e-commerce, booking, and customer management solutions, as well as the website builder itself.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Develop/maintain modern React.ts applications utilizing MSW, RTL, Redux, and other technologies
    \item Develop/maintain modern PHP backend applications and RESTful APIs using Symfony
    \item Maintain various large legacy applications written using a variety of technologies such as silex and backbone js
    \item Implementing functional testing strategies utilizing Mocha, PHPUnit, Jest, RTL, and other tools
\end{itemize}
\\

% WCBS
{\bf WCBS}\\
2021--2022\\
&{\bf Full Stack Developer}\newline
Part of an agile team working remotely to develop a modern cloud native Management Information System (MIS) solution for a large number of schools. Operated using a broad tech stack, including Vue3, Symfony, and Docker.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Develop a Vue.ts frontend and a Symfony RESTful API
	\item Ensuring code quality through Jest/PHPUnit tests and code review
	\item Deploying releases through the various environments
	\item CI/CD through GitHub and Jenkins
	\item DevOps through the GCP, Kubernetes, and Docker
	\item Database and entity management through Doctrine ORM
\end{itemize}
\\

% Tutoring
{\bf Aberystwyth University}\\
2017--2021\\
&{\bf University Tutor}\newline
Tutored Computer Science university students in a variety of different computer science contexts.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Running workshops, lectures, and tuition groups with undergraduate students
	\item Hosting advisory sessions to help students through a wide range of problems
	\item One-to-one teaching
	\item Grading and supplying feedback to assignments and coursework
\end{itemize}
\\

% Lexis Nexis
{\bf Lexis Nexis Risk Solutions}\\
2016\\
&{\bf PHP Software Engineer}\newline
Operated with a team of developers/testers to implement industry quality software through a Zend Framework. Responsible for pushing code to a Jenkins CI server, and ensuring code quality through custom codesniffers and unit/integration tests.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Working in an Agile team delivering user stories through sprints
    \item Peer reviewing code
    \item Developing features involving both front-end and back-end aspects
\end{itemize}
\end{longtable}

% education
\section*{Education}
\begin{longtable}{L!{\VRule}R}

% PhD
{\bf Aberystwyth University}\\
&{\bf PhD Topological Mapping with Swarm Robotics}\newline
Worked on novel solutions for the topological multi-agent SLAM problem, using a swarm of agents to map out an environment. Involved with writing ROS modules to achieve challenging tasks in languages such as C++, Java, and Python.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Developing a simulator for robotic operations
	\item Innovating novel solutions to the multi-agent SLAM problem
	\item Communicating advanced and technical work
\end{itemize}
\\

% BSc Computer Science
{\bf Aberystwyth University}\\
&{\bf BSc Computer Science}\newline
During the degree, a wide range of technologies were studied which are still utilised today.

\vspace{-3mm}
\paragraph{Modules:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Web programming
    \item Java, C, and C++ programming paradigms
    \item Software development lifecycle
    \item Human computer interface and human computer interaction
    \item Agile methodologies
    \item Advanced computer graphics
\end{itemize}
\\

\end{longtable}

% personal details
\section*{Personal Details}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Contributor to Nixpkgs
    \item Experience with using ROS to control robots in simulation and real world application.
	\item Friendly and approachable personality, with confidence to ask questions and collaborate with others.
	\item Full UK driving licence.
\end{itemize}

\end{document}
